\documentclass{resume} 
\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} 
% \usepackage{hyperref}
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Kyle Bower}
\address{+1\;(604)\;401-4234 \\ kyle.bower@mail.utoronto.ca}

\begin{document}

\begin{rSection}{Education}

\textbf{University of Toronto} \hfill {\normalfont Sep 2018 -- May 2023} \\
{\normalfont \textit{Doctor of Philosophy, Mathematics}} \\
\textbf{University of Toronto} \hfill {\normalfont Sep 2017 -- Aug 2018} \\
{\normalfont \textit{Master of Science, Mathematics}} \\
\textbf{University of British Columbia} \hfill {\normalfont Sep 2013 -- Apr 2017}\\
{\normalfont \textit{Bachelor of Science, Honours Physics and Mathematics}}

\end{rSection}

% \begin{rSection}{Career Objective}
%  To work for an organization which provides me the opportunity to improve my skills and knowledge to grow along with the organization objective.
% \end{rSection}

\begin{rSection}{Work Experience}

\begin{rSubsection}{Head Graduate Teaching Assistant}{Sep 2017 -- Present}{University of Toronto}{Toronto, ON}
    \item Developed a script to automatically assign 1,500+ students to tutorial sections. (Python)
    \item Mentored 100+ students each term in weekly tutorials, held office hours, invigilated exams, and graded tests for undergraduate math courses.
    \item Led orientation and regular training for aspiring and new teaching assistants.
\end{rSubsection}

\begin{rSubsection}{Cryptanalyst Summer Intern}{May 2017 -- Aug 2017}{Communications Security Establishment}{Ottawa, ON}
    \item Performed cryptologic research, designed, developed, assessed, and attacked cryptographic algorithms and protocols to support Government of Canada Intelligence and Cyber Defense requirements.
    \item Attended the Selected Areas in Cryptography Summer School at the University of Ottawa to learn about symmetric key, public key, and post-quantum cryptography.
\end{rSubsection}

\begin{rSubsection}{Undergraduate Student Researcher}{May 2016 -- Aug 2016}{Natural Sciences and Engineering Research Council of Canada}{Vancouver, BC}
    \item Conducted independent research on the Min protein system involved in bacterial cell division under the supervision of Dr. Eric Cytrynbaum.
    \item Simulated cell-scale biochemical reactions to capture the natural stochasticity of a biological cell. (Smoldyn)
    \item Employed numerical methods to solve a system of partial differential equations that described the biochemical reactions occurring in the cell. (MATLAB/GNU Octave)
\end{rSubsection}

\begin{rSubsection}{Undergraduate Teaching Assistant}{Sep 2015 -- Apr 2017}{University of British Columbia}{Vancouver, BC}
    \item Invigilated exams and graded tests for undergraduate math courses.
\end{rSubsection}

\begin{rSubsection}{Lifeguard/Swim Instructor}{Nov 2013 -- Apr 2017}{City of Richmond}{Richmond, BC}
    \item Supervised patrons to ensure a safe and enjoyable aquatic environment.
    \item Taught swimming and water safety to students of all ages and abilities.
\end{rSubsection}

\end{rSection}

\begin{rSection}{Technical Skills}

{\normalfont Experience with Python, MATLAB, LaTeX, UNIX, Linux, GitHub.}

\end{rSection}

\end{document}
